### 2020-12-30 cleave.tex
more

    This agnosticism is achieved through careful abstraction of the the system into a well-defined API based around the following components:
    \begin{itemize}
        \item A \texttt{State} object, which implements the discrete-time evolution of the physical system being controlled.
        This object also holds a number of named properties that can be measured or actuated upon.
        \item An arbitrary number of \texttt{Sensor} objects which measure named properties of the \texttt{State}, and potentially transform them (for instance, to add noise).
        \item A \texttt{Controller} object which receives values of named properties processed by the \texttt{Sensor} objects and returns new values for the named properties of the \texttt{State} that can be actuated upon.
        \item Finally, an arbitrary number of \texttt{Actuator} objects which receive the values generated by the \texttt{Controller} and process them before passing them on the \texttt{State}.
    \end{itemize}
    Users implement their desired behavior by extending the abstract base classes defining these components provided by the framework.

@@

>>>>

    \item[API based on well-defined components.]
    The previously mentioned agnosticism is achieved through careful abstraction of the the system into an API based around the following components:
    \begin{itemize}
        \item A \texttt{State} object, which implements the discrete-time evolution of the physical system being controlled.
        This object also holds a number of named properties that can be measured or actuated upon.
        \item An arbitrary number of \texttt{Sensor} objects which measure named properties of the \texttt{State}, and potentially transform them (for instance, to add noise).
        \item A \texttt{Controller} object which receives values of named properties processed by the \texttt{Sensor} objects and returns new values for the named properties of the \texttt{State} that can be actuated upon.
        \item Finally, an arbitrary number of \texttt{Actuator} objects which receive the values generated by the \texttt{Controller} and process them before passing them on the \texttt{State}.
    \end{itemize}
    Users implement their desired behavior by extending the abstract base classes defining these components provided by the framework.

    \item[Plain Python configuration.]
    As mentioned above, users implement their desired behavior for the core components by extending classes provided by the framework.
    This is done in configuration files written in full-featured Python simply defining a number of required top-level variables and which are then passed to the main script provided with CLEAVE.
    This allows for easy configuration of arbitrarily complex emulations.

@@

\begin{figure}
    \centering
    \includegraphics[width=3cm]{example-image-a}
    \caption{Execution flow of a time step in CLEAVE.}
\end{figure}

\begin{listing}
    \begin{minted}[linenos=true,
        breaklines, 
        breakafter=d,
        fontsize=\small]{Python}
from cleave.api.plant import SimpleConstantActuator, SimpleSensor
from cleave.impl.inverted_pendulum import InvPendulumState

host = 'localhost'
port = 8080

controller_class = 'InvPendulumController'

tick_rate = 100
emu_duration = '30m'

state = InvPendulumState(fail_angle_rad=-1)

sensors = [
    SimpleSensor('position', 100),
    SimpleSensor('speed', 100),
    SimpleSensor('angle', 100),
    SimpleSensor('ang_vel', 100),
]

actuators = [
    SimpleConstantActuator(initial_value=0, prop_name='force')
]

output_dir = './plant_metrics'
    \end{minted}
    \caption{Example configuration file.}
    \label{lst:config}
\end{listing}
